Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-13 paper.tex
update first page

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers. One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions. Optimisation problems are another challenge. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS. This paper develops a more applicable way of measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented paradigm of computing. Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.

>>>>

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet non-functional requirement of service users. e.g minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are very few works concerns both quality of semantic matching and quality of services at the same time. Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement. We will evaluate our approach utilising a semantic benchmark dataset.

\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) is capable of abstractly realising service-oriented computing. Since its inception, SOA has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.
